U.S. Labour Market Resilience

### 2024-03-18 paper/paper.qmd
Update paper

From the dataset, we used the variable “response” to collect the respondent’s responses. For clarity, the variable was renamed to “work hours” as the respondent’s response was the number of hours they worked. Another variable used is “year”. The purpose of this variable is to collect the year the survey was conducted.

@@

| Variable | New Name   | Description                     | Example |
|----------|------------|---------------------------------|---------|
| response | work hours | Respondent's response           | 23      |
| year     | year       | The year of the survey recorded | 2007    |

@@

```{r}
#| label: fig-hour-working-percentage
#| fig-cap: Average Working Hours Percentages 
#| echo: false
#| warning: false
#| message: false

@@

@@

@fig-demographic-comparison presents a comparison of average ages across different years, specifically for 1998, 2008, 2010, 2018, and 2021. The y-axis represents the average age, and the x-axis denotes the years. The bars show a slight decrease in the average age in 2021 compared to the previous years, suggesting a younger demographic in the most recent year displayed. It also illustrates the percentage of females within the data for the same years as shown in @fig-demographic-comparison. The y-axis indicates the percentage of females, while the x-axis represents the years. The bars are relatively even, demonstrating a consistent representation of females across the selected years, with a very slight variation.

Both figures are titled "Working Hours Comparisons with Demographic factors," implying that the data presented may be used to analyze the relationship between demographic characteristics (age and gender) and working hours, although the specific hours worked are not shown in these charts. The consistent layout and design of the charts facilitate a clear and direct comparison of demographic trends over the years.

@@

Our analysis grounded in the rich dataset provided by the General Social Survey (GSS) [^1], navigates through a complex terrain of labour market dynamics in the wake of economic crises. However, as mentioned in the @sec-data section, several limitations inherent to the dataset and the broader research approach necessitate a cautious interpretation of our findings.

@@

Finally, our paper also has certain limitations in processing data as shown in @sec-data section. One limitation stems from our decision to analyze the years immediately following the economic crisis (2010 and 2021) rather than the year immediately following the recession itself. This choice was made partly because of the lack of data for 2009 in the General Social Survey (GSS), necessitating the need to use 2010 (the second year of the economic crisis) as a proxy to measure the post-crisis impact of the 2008 financial recession. Likewise, given the unprecedented impact of the COVID-19 pandemic in 2020, the selection of 2021 was intended to capture its consequences rather than 2022, which could be compared to the 2010 selection.

>>>>

From the dataset, we used the variable “response” to collect the respondent’s responses. For clarity, the variable was renamed to “work hours” as the respondent’s response was the number of hours they worked. Another variable used is “year”. The purpose of this variable is to collect the year the survey was conducted. To collect demographic data, specifically age and gender, the datasets “age” and “sex” were used. The two datasets are used to further analyze age groups and genders to working hours.

@@

| Variable | New Name   | Description                     | Example |
|----------|------------|---------------------------------|---------|
| response | work hours | Respondent's response           | 23      |
| year     | year       | The year of the survey recorded | 2007    |
| AGE      | AGE        | The age of the respondents      | 23      |
| SEX      | SEX        | The gender of the respondents   | MALE    |

@@

## Percentage of Working Hours Responses
```{r}
#| label: fig-hour-working-percentage
#| fig-cap: Average Working Hours Percentages 
#| echo: false
#| warning: false
#| message: false

@@

## Demographic Factors

@@

@fig-demographic-comparison presents a comparison of average ages across different years, specifically for 1998, 2008, 2010, 2018, and 2021. The bars show a slight decrease in the average age in 2021 compared to the previous years, suggesting a younger demographic in the most recent year displayed. It illustrates the percentage of females within the data for the same years as shown in @fig-demographic-comparison as well. The bars are relatively even, demonstrating a consistent representation of females across the selected years, with a very slight variation.

Both @fig-demographic-comparison-1 and @fig-demographic-comparison-2 analyze the relationship between demographic characteristics (age and gender) and working hours. The demographic factors do not vary dramatically, indicating that age and gender may not play a significant role in terms of work hours in a week.

@@

Our analysis grounded in the rich dataset provided by the General Social Survey (GSS) [^1], navigates through a complex terrain of labour market dynamics in the wake of economic crises. However, as mentioned in the [Data] section, several limitations inherent to the dataset and the broader research approach necessitate a cautious interpretation of our findings.

@@

Finally, our paper also has certain limitations in processing data as shown in [Data] section. One limitation stems from our decision to analyze the years immediately following the economic crisis (2010 and 2021) rather than the year immediately following the recession itself. This choice was made partly because of the lack of data for 2009 in the General Social Survey (GSS), necessitating the need to use 2010 (the second year of the economic crisis) as a proxy to measure the post-crisis impact of the 2008 financial recession. Likewise, given the unprecedented impact of the COVID-19 pandemic in 2020, the selection of 2021 was intended to capture its consequences rather than 2022, which could be compared to the 2010 selection.
